-

### 2023-01-17 DRAFT_homogeneous_impact_areas.Rmd
feat: Vectorize infra

<!-- Load all you dependencies here -->
```{r setup, include=FALSE}
library(knitr)
knitr::opts_chunk$set(echo = TRUE)
library(sf)
library(tmap)
library(dplyr)
#library(osmplotr)
```

@@

## Discretize the entire map

##

>>>>

<!-- Load all you dependencies here -->
```{r setup, include=FALSE}
library(knitr)
knitr::opts_chunk$set(echo = TRUE)
library(sf)
library(tmap)
library(dplyr)
library(stars)
#library(osmplotr)
```

@@

### Aggregate
The resolution in this map is more than we need, and the size of the data implies that the next step, the vectorization, would take too long.
We therefore aggregate, ar reduce the resolution.

```{r}
dim <- st_dimensions(infra)
paste("Resolution is", dim$x$delta, "by", dim$x$delta, "meters")
```

```{r}
infra_trd_reclassed_agg <- st_warp(infra_trd_reclassed, cellsize = c(1000, 1000), 
                                   crs = st_crs(infra_trd_reclassed), 
                                   use_gdal = TRUE,
                                   method = "average")
```

```{r}
dim <- st_dimensions(infra_trd_reclassed_agg)
paste("Resolution is", dim$x$delta, "by", dim$x$delta, "meters")
```

Each cell is no the average of the aggregated cells, and hence the value is continous again. Let's make it discrete.
```{r}
names(infra_trd_reclassed_agg) <- "infrastructureIndex"
infra_trd_reclassed_agg <-  infra_trd_reclassed_agg %>%
  mutate(infrastructureIndex = case_when(
    infrastructureIndex < 1 ~ 0,
    infrastructureIndex < 6 ~ 1,
    infrastructureIndex < 9 ~ 2,
    infrastructureIndex >= 9 ~ 3
  ))
```

```{r, fig.cap="Infrastrcture indeks over Trondheim on a four-step discrete scale, aggregated to 1x1 km resolution using the mean function."}
tm_shape(infra_trd_reclassed_agg)+
  tm_raster(title="Infrastructure Index",
            style="cat")+
  tm_layout(legend.outside = T)+
  tm_shape(hw_utm)+
  tm_lines(col="white")
```

This resolution is more that good enough for our purpose here.

## Aggregate the entire map to 1x1 km
```{r}
# runtime about 30 sec
infra_agg <- st_warp(infra, cellsize = c(1000, 1000), 
                                   crs = st_crs(infra), 
                                   use_gdal = TRUE,
                                   method = "average")
```

## Discretize the entire map
```{r}
names(infra_agg) <- "infrastructureIndex"

infra_agg_discrete <- infra_agg %>%
  mutate(infrastructureIndex = case_when(
    infrastructureIndex < 1 ~ 0,
    infrastructureIndex < 6 ~ 1,
    infrastructureIndex < 9 ~ 2,
    infrastructureIndex >= 9 ~ 3
  ))
```

## Vectorize
This step might seem rather stupid. We want to vectorize a rather large raster. This makes it a quite big data object.
The reason is that there is no really good way to burn polygon data on to raster grid cells after the disuse of the
`{raster}` package. It was not straight forward then either. But calculating intersections between polygons is very fast and easy.

```{r}
infra_agg_discrete_vect <- eaTools::ea_homogeneous_area(infra_agg_discrete)
```

Let's plot this now.
First. lets crop it to reduce computation time.
```{r}
infra_agg_discrete_vect_trd <- st_crop(infra_agg_discrete_vect, myBB)
```

```{r}
tmap_mode("view")
tm_shape(infra_agg_discrete_vect_trd)+
  tm_polygons(col="infrastructureIndex")
```
